Joshua 2.0: A Toolkit for Parsing-Based Machine Translation \\with Syntax, Semirings, Discriminative Training and Other Goodies

### 2010-04-23 papers/wmt10/joshua-progress.tex
anni section added
git-svn-id: https://joshua.svn.sourceforge.net/svnroot/joshua/branches/publications@1630 0ae5e6b2-d358-4f09-a895-f82f13dd62a4

\section{Specifying Constraints on Rules}
\todo{anni}

@@

We have introduced tools for visualizing two of the main data structures used
in Joshua \cite{PBML-2010-Joshua-visualization}. Each visualization tool is implemented as a
stand-alone program that hooks into the pipeline, but they are distributed with
Joshua. The first program is a hypergraph visualizer. The user can choose from
a set of input sentences, then call the decoder to build the hypergraph.

>>>>

\section{Specifying Constraints on Rules}

Integrating output from specialized modules (like transliterators, morphological analyzers, and modality translators) into the MT pipeline can improve translation performance, particularly in low-resource settings. We have implemented this functionality in Joshua by supporting an XML format for proposing alternate translation rules (constraints) for a particular word span to the decoder \cite{pbml-2010-Joshua-modules}. That is, processing that is separate from the MT engine can suggest translations for some set of source side words and phrases. The XML format allows for both hard constraints, which must be used, and soft constraints, which compete with standard extracted translation rules, as well as specifying associated feature weights. We modified the chart-based decoder to support these constraints.

@@

We have introduced tools for visualizing two of the main data structures used
in Joshua \cite{PBML-2010-Joshua-transliteration}. Each visualization tool is implemented as a
stand-alone program that hooks into the pipeline, but they are distributed with
Joshua. The first program is a hypergraph visualizer. The user can choose from
a set of input sentences, then call the decoder to build the hypergraph.
